\cvsection{Work Experience}

\begin{cventries}
  \cventry
    {Software Engineer} % Job title
    {Western Digital Corporation} % Organization
    {Milpitas, CA} % Location
    {August 2022 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Perform initial failure analysis/triage of automated tests every morning and create/update Jiras for the relevant teams.}
        \item {Modify/port Continuous Integration scripts.}
        \item {Run tests on drives and report results (pass/fail, error message, etc.)}
        \item {Bring up lab systems, including bench machines and Raspberry Pis.}
      \end{cvitems}
    }

  \cventry
    {Embedded Systems Design Lab Tutor} % Job title
    {UC Santa Cruz} % Organization
    {Santa Cruz, CA} % Location
    {September 2021 - November 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led 3 lab sections a week with 1-2 other tutors.}
        \item {Assisted around 20 students each section on their lab by answering questions and providing guidance for debugging.}
        \item {Performed check-offs and graded submissions.}
      \end{cvitems}
    }

  \cventry
    {Optometric Technician} % Job title
    {San Jose Eyecare} % Organization
    {San Jose, CA} % Location
    {June 2016 - Sept 2021 (Summers)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Operated diagnostic equipment.}
        \item {Authorized and checked coverage of patient insurance.}
        \item {Scheduled appointments, took calls, handled pickups, and other front-desk tasks.}
      \end{cvitems}
    }
\end{cventries}
