\cvsection{Projects}
% https://zety.com/blog/projects-on-resume#:~:text=Projects%20can%20be%20listed%20on,in%20the%20education%20resume%20section.

\begin{cventries}
  \cventry
    {Embedded Systems Design} % Empty position
    {Simple Two Channel Oscilloscope} % Project
    {Santa Cruz, CA} % Empty location
    {September 2021 - June 2021} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Displayed wave-forms and frequency readings onto an LCD screen. Supported vertical and horizontal scaling.}
        \item {Read voltage values on 2 GPIO pins using an ADC. Data points are transferred from the ADC buffer to ping-pong buffers via DMA.}
        \item {Processing is done on the ping-pong buffers to calculate the frequency, select appropriate data points to render, and detect triggers.}
        \item {User input enabled through knobs and command line. Knobs are potentiometers monitored by the ADC. Command line communicates over UART and is parsed on the microcontroller.}
      	\item {Designed for the PSoC-6 microcontroller and written in C.}
      \end{cvitems}
    }

  \cventry
    {Embedded Systems Design}
    {Quadruple Software UART}
    {Santa Cruz, CA}
    {September 2021 - June 2021}
    {
        \begin{cvitems}
          \item {Optimization exercise to implement four UARTs in software and on just the CM4 core.}
          \item {UARTs operated concurrently as tasks in FreeRTOS.}
          \item {Written in C for the PSoC-6 microcontroller.}
        \end{cvitems}
    }
       
  \cventry
    {Principles of Computer Systems Design} % Empty position
    {Pintos Modification Labs} % Project
    {Santa Cruz, CA} % Empty location
    {January 2022 - March 2022} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Improve and implement aspects of the Pintos operating system including the ability to block threads, priority-based thread scheduling, and priority donation.}
        \item {Dealt with multi-threading and used concurrency primitives. Also, implemented condition variables and locks into Pintos using the OS's semaphore implementation.}
        \item {Written in C. Version control with Git. Debugging done with GDB.}
      \end{cvitems}
    }
    
  \cventry
    {Engineering Design Project} % Empty position
    {PLUX: Smart Outlet} % Project
    {Santa Cruz, CA} % Empty location
    {January 2022 - June 2022} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Worked on a team to create an IoT device that plugs into an outlet and allows for remote control and monitoring of power consumption.}
        \item {Programmed an ESP~32 to connect to WiFi and publish/receive MQTT messages. Programmed in C++ with the Arduino IDE.}
        \item {Used Python to create an MQTT client that parses messages and writes to an SQLite3 database on an Oracle Cloud instance.}
        \item {Designed the architecture and protocol for sending messages between the smart plug, server, and web-client.}
      \end{cvitems}
    }

  \cventry
    {Not affiliated with UCSC} % Empty position
    {Unnamed Bus System Project} % Project
    {Santa Cruz, CA} % Empty location
    {January 2021 - June 2022} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Contributed to the creation of an integrated hardware and software system to track a transit bus's position and  route, as well as provide a console for the bus driver to interact with the system.}
      	\item {Designed and wrote the program flow for the Driver Console in C. Uses a simplified state-machine design pattern that makes use of function pointers to encapsulate each state.}
      	\item {Use CMake to cross compile for RP2040 on the Raspberry Pi Pico.}
      \end{cvitems}
    }
    
  \cventry
    {Introduction to Software Engineering}
    {BAM! File Sharing Web App}
    {Santa Cruz, CA}
    {March 2022 - June 2022}
    {
        \begin{cvitems}
            \item {Worked on a Scrum team as Product Owner and followed Scrum principles.}
            \item {Is a web app that allows devices to share files by fist-bumping. Files are sent peer-to-peer via WebTorrent.}
            \item {Designed and wrote the back-end architecture and the logic for connecting two clients and sending files.}
            \item {Built with React, Express, and NodeJS.}
        \end{cvitems}
    }

  \cventry
    {Network Programming}
    {Reliable File transfer protocol}
    {Santa Cruz, CA}
    {January 2022 - March 2022}
    {
        \begin{cvitems}
            \item {Created and implemented a protocol for reliable data transfer between a server and client via UDP.}
            \item {Can handle multiple clients concurrently.}
            \item {Improved performance by using a sliding window and buffering out of order packets.}        \end{cvitems}
    }

\end{cventries}